Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2024-01-02 output/paper/_tables.qmd
First round of modifications for tables and figures done.

>>>>

::: {#tbl-met-new-desc}
```{r met-new-desc}
metabolites <- load_steroids()
scores <- create_steroid_scores(dat = metabolites$metabolome) |>
  tidylog::select(
    HelixID,
    cortisol_production, cortisone_production,
    corticosterone_production
  )
scores <- myphd::extract_cohort(
  dat = scores,
  id_var = "HelixID",
  st = 1, en = 3
) |>
  tidylog::select(-HelixID) |>
  tidylog::mutate(
    cohort = dplyr::case_when(
      cohort == "EDE" ~ "EDEN",
      cohort == "KAN" ~ "KANC",
      cohort == "MOB" ~ "MOBA",
      cohort == "RHE" ~ "RHEA",
      .default = cohort
    )
  ) |>
  tidylog::rename(
    "cortisol production" = "cortisol_production",
    "cortisone production" = "cortisone_production",
    "corticosterone production" = "corticosterone_production"
  )

scores |>
  gtsummary::tbl_summary(
    by = "cohort"
  ) |>
  gtsummary::add_overall() |>
  gtsummary::as_gt() |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Participants derived glucocorticosteroids concentrations, by cohort and overall (HELIX Study; 2013-2016).**
:::

### 2024-01-02 output/paper/manuscript.qmd
First round of modifications for tables and figures done.

```{r vars-methods}
source(here::here("R/dictionaries.R"))
source(here::here("R/data.R"))
source(here::here("R/proc_res.R"))

@@

Levels of unprocessed non-persistent \acr{edcs} and glucocorticosteroids, by cohort and overall, are presented in @tbl-edc-desc and @tbl-met-desc, respectively.

@@

[] EDCs to HITRTSE
[X] EDCs to CORT.
[] CORT. to HITRTSE

>>>>

```{r vars-methods}
source(here::here("R/dictionaries.R"))
source(here::here("R/data.R"))
source(here::here("R/utils.R"))
source(here::here("R/proc_res.R"))

@@

Levels of unprocessed non-persistent \acr{edcs} and glucocorticosteroids, by cohort and overall, are presented in @tbl-edc-desc, @tbl-met-desc, and @tbl-met-new-desc.

@@

[] EDCs to HITRTSE
[] EDCs to CORT.
[] CORT. to HITRTSE
